### 2019-10-14 paper/abstract.tex
Osama's changes after whole manuscript review including answers #13

\begin{abstract}
Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation-resistance. The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as start-up fissile material. Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials. This work investigated the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at start-up: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} spent fuel with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF} and finally $^{233}$U.
The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}. The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U have been studied in the present work. The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for $^{233}$U start-up fuel. Finally, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
\end{abstract}

>>>>

\begin{abstract}
Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation-resistance. The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as startup fissile material. Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials. This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF} and finally $^{233}$U.
The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}. The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U have been studied in the present work. Additionally, the neutron spectrum shift during the reactor operation was calculated. The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel. Finally, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
\end{abstract}

### 2019-10-14 paper/introduction.tex
Osama's changes after whole manuscript review including answers #13

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation
nuclear systems. These goals have been defined in four broad areas: safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}. The \gls{MSR} has many advantages that consistent
with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online
reprocessing and refueling, excellent neutron economy and operation near
atmospheric
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}.
Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl).
This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
circulates through the core and allows transferring fission heat from reactor
core to heat exchanger.

@@

Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial
fissile materials \cite{betzler2016modeling}. They concluded that the 
plutonium vector extracted from LWR SF is the best alternative source to 
$^{233}$U because it has the highest ratio of fissile isotopes
\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for
the thorium fuel cycle transition in \gls{TMSR}: (1) in-core transition and 
(2) ex-core transition. In the first approach, the TMSR is launched with 
existing fissile material and thorium as a fertile material; then the 
$^{233}$U bred from thorium is rerouted into the core to maintain criticality. 
In contrast, the second approache tends to store produced $^{233}$U out of the 
core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel
cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU}
as startup fuel. They concluded that the transition to thorium fuel cycle can
be achieved in thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.

Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR}
under different launching scenarios (e.g., enriched uranium and TRU) they concluded that starting the Thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling,
ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
heuer2014towards,fiorina2013investigation}, while little focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary,
zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other
fissile materials (except $^{233}$U) was not studied before. Therefore,
the main object of the present paper is to discuss the simulation of the
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
different initial fissile materials and without any external feed of $^{233}$U
to achieve the thorium fuel cycle transition. We investigated five different
initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed scenarios were selected:

\begin{itemize}
	\item Continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}

All calculations presented in the present paper were performed using SERPENT-2 version 2.1.30. We used the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling. SERPENT-2 uses an internal calculation routine for solving the set of Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}. Additionally, SERPENT-2 allows us to conduct the burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.

This present paper is organized as follows: after an introduction about 
\gls{MSR} systems, the model description is discussed in section 2. 
Methodology and tools is descried in section 3. Extraction and feed mechanisms 
are addressed in section 4. Section 5 focuses on the results and discussion. 
Finally, section 6 highlights the conclusions.

>>>>

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation
nuclear systems. These goals have been defined in four broad areas: safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}. The \gls{MSR} has many advantages that consistent
with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online
reprocessing and refueling, excellent neutron economy and operation near
atmospheric
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}.
Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl).
This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
circulates through the core and allows transferring fission heat from reactor
core to \glspl{IHX}.

@@

Betzler \emph{et al.} (2016), discussed the simulation of the startup of a MSBR unit
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent nuclear fuel (SNF) as initial
fissile materials \cite{betzler2016modeling}. They concluded that the 
plutonium vector extracted from LWR SNF is the best alternative source to 
$^{233}$U because it has high ratio of fissile isotopes
\cite{betzler2016modeling}. Zou \emph{et al.} (2018), introduced two approaches for
the thorium fuel cycle transition in \gls{TMSR}: (1) in-core transition and 
(2) ex-core transition. In the first approach, the TMSR is launched with 
existing fissile material and thorium as a fertile material; then the 
$^{233}$U bred from thorium is rerouted into the core to maintain criticality. 
In contrast, the second approache tends to store produced $^{233}$U out of the 
core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Additionally, Zou \emph{et al.} (2018), studied the transitioning to thorium fuel
cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU}
as startup fuel. They concluded that the transition to thorium fuel cycle can
be achieved in thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.

Heuer \emph{et al.} (2014), discussed the transition characteristics of the \gls{MSFR}
under different launching scenarios (e.g., enriched uranium and TRU) they concluded that starting the thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
researches focus on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	fiorina2013investigation}, while little focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
	zou2018transition,zou2018preliminary}. Nevertheless, simulating the operation of the \gls{SD-TMSR} concept with other
fissile materials (except $^{233}$U) was not studied before. Therefore,
the main object of the present paper is to discuss the simulation of the
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
different initial fissile materials and without any external feed of $^{233}$U
to achieve the thorium fuel cycle transition. We investigated five different
initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SNF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed mechanisms were selected:

\begin{itemize}
	\item Thorium feed mechanism: continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Non-thorium feed mechanism: continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}

All calculations presented in the present paper were performed using SERPENT-2 version 2.1.30 \cite{leppanen2014serpent}. We used the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling. SERPENT-2 uses an internal calculation routine for solving the set of Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}. Additionally, SERPENT-2 allows us to conduct the burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.

This present paper is organized as follows: after an introduction about 
\gls{MSR} systems, the model description is discussed in section \ref{Model-description}. 
Methodology and tools is descried in section \ref{Methodology-and-tools}. Extraction and feed mechanisms 
are addressed in section  \ref{Feed-and-extraction-rates}. Section \ref{Results-and-discussion} focuses on the results and discussion. 
Finally, section \ref{Conclusion} highlights the conclusions.
